---
title: "homework 2"
author: "Sze Pui Tsang"
date: "10/9/2021"
output: html_document
---

```{r library}
library(tidyverse)
library(readxl)
library(dplyr)
```

# Problem 1

```{r define path}
path_of_data = "C:/Users/Yang/Desktop/st3340_p8105_classex/data_hw2/Trash-Wheel-Collection-Totals-7-2020-2.xlsx"
```

```{r import the dataframe}
mr_trash_df = 
  read_excel( 
    path = path_of_data,
    sheet = "Mr. Trash Wheel"
    )
```

We have to clean the table by cleaning up the variable names,
omitting the missing value abd rounding the number of sport balls to 
the nearest integer

```{r clean the data frame}
clean_mr_trash_df = mr_trash_df %>%
  janitor::clean_names() %>%
  drop_na(dumpster) %>%
  mutate ( 
    sports_balls = round(sports_balls, digits = 0)
  )
  
``` 

Read and clean precipitation data for 2018. 
```{r Read data for 2018}
precipitation_18_df= read_excel( 
    path = path_of_data,
    sheet = "2018 Precipitation",
    range = "A2:B14")
```

```{r clean data for 2018}
precipitation_18_df = precipitation_18_df %>%
  janitor :: clean_names() %>%
  drop_na(month) %>%
  mutate(year =2018) %>%
  relocate(year, .before = "month")%>%
  mutate(
    total = round(total, digit = 1)
  )
```

Read and clean precipitation data for 2019.
```{r clean data for 2019}
precipitation_19_df= read_excel( 
    path = path_of_data,
    sheet = "2019 Precipitation",
    range = "A2:B14")%>%
  janitor :: clean_names() %>%
  drop_na(month)%>%
  mutate(year =2019)%>%
  relocate(year, .before = "month")%>%
  mutate(
    total = round(total, digit = 1)
  )
```

Combind precipitation dataset and convert month into a character variable
```{r combind the two dataset}
month_df =
  tibble(
    month = 1:12,
    month_name = month.name)

precipitation_18and19_df = bind_rows(precipitation_18_df,precipitation_19_df)

precipitation_18and19_df = left_join(precipitation_18and19_df, month_df, by="month")
```

view the dataset
```{r}
median(precipitation_19_df$total)
sum(precipitation_18_df$total)
```

The median number of sports balls in a dumpster in 2019 was 3.35
The total precipitation in 2018 was 70.3 inches 